Value Ordering, Discrepancies, and Restarts for Subgraph Algorithms

### 2018-01-18 long-talk/talk.tex
Just a little bit more
Another plot

    \includegraphics<1>{gen-graph-value-ordering-heuristics.pdf}

@@

    \only<1>{
    \begin{itemize}
        \item Select a vertex $v'$ from the chosen domain $D_v$ with
            probability \[ p(v') = \frac{2^{\deg(v')}}{\sum_{w \in D_v}{2^{\deg(w)}}} \text{.} \]
        \item Looks a lot like $\mathit{softmax}$, which uses base $e$.
    \end{itemize}
    }%
    \includegraphics<2>{gen-graph-value-ordering-heuristics-biased.pdf}

>>>>

    \includegraphics<1>{gen-graph-value-ordering-heuristics.pdf}%
    \includegraphics<2>{gen-graph-value-ordering-heuristics-unsat.pdf}%

@@

    \only<1>{
    \begin{itemize}
        \item Select a vertex $v'$ from the chosen domain $D_v$ with
            probability \[ p(v') = \frac{2^{\deg(v')}}{\sum_{w \in D_v}{2^{\deg(w)}}} \text{.} \]
        \item Looks a lot like $\mathit{softmax}$, which uses base $e$.
    \end{itemize}
    }%
    \includegraphics<2>{gen-graph-value-ordering-heuristics-biased.pdf}%
    \includegraphics<3>{gen-graph-scatter-biased.pdf}
